---
title: "Survey"
author: "SP"
date: "24 October 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
#Survey - F2F

```{r}
svyF2F<-svydesign(ids=~ID, strata=~ADM1_NAME, fpc=~PopRural, data=SETSAN2, nest=TRUE)
summary(svyF2F)
```
Weighted mean HDDS for F2F only rural
```{r}
mean.HDDS.F2Fsvy<-svymean(~HDDS, svyF2F)
mean.HDDS.F2Fsvy
```
UN-Weighted mean HDDS for F2F only rural
```{r}
mean.HDDS.F2F<-mean(SETSAN$HDDS)
mean.HDDS.F2F
```
Mean HDDS by ADM1
```{r}
svyby(~HDDS, by=~ADM1_NAME, design=svyF2F, FUN=svymean)
```

#Survey - CATI
```{r}
svymVAM<-svydesign(ids=~RspID, strata=~ADM1_NAME, fpc=~PopRural, data=mVAMRural, nest=TRUE)
summary(svymVAM)

install.packages('ddply')
install.packages("dplyr")
install.packages('plyr')
library(ddply)
library(plyr)

x <- ddply(svymVAM$variables, 'ADM1_NAME', transform, SelectWtNorm = scale(SelectWt,center = FALSE, scale = mean(SelectWt)))$SelectWtNorm
svymVAM$prob <- svymVAM$prob/x
```

#For Post-Stratification
```{r}
pop<-c(1168156,1467952)
ADM1_NAME<-c("Inhambane","Gaza")
rurpop<-data.frame(ADM1_NAME,pop)

svymVAM <- postStratify(des=svymVAM,strata =~ADM1_NAME,pop=rurpop)
summary(svymVAM)

totPop <- sum(weights(svymVAM))

```
```{r}

calbrDFIncomeSrc <- prop.table(svytable(~ADM1_NAME+IncomeSrc,svyF2F))
colnames(calbrDFIncomeSrc) <- c('AgFish',"Salary","SelfEmploy","CasualLabour")

svyF2F$variables$Gender <- droplevels(svyF2F$variables$Gender)
calbrDFGender <- prop.table(svytable(~ADM1_NAME+Gender,svyF2F))

calbrDFGenderIncome <- prop.table(svytable(~Gender+IncomeSrc,svyF2F))
colnames(calbrDFGenderIncome) <- c('AgFish',"Salary","SelfEmploy","CasualLabour")
#calbrDFIncomeSrc[,2]<- round(calbrDFIncomeSrc[,2]*totPop)
```

```{r}
#calibration performed by raking
svymVAM$variables$IncomeSrc2 <- svymVAM$variables$IncomeSrc
svymVAM$variables$IncomeSrc[svymVAM$variables$IncomeSrc=="Assistance"] <- "CasualLabour"
svymVAM$variables$IncomeSrc <- droplevels(svymVAM$variables$IncomeSrc)
svymVAM2 <-rake(svymVAM,sample.margins=list(~ADM1_NAME+IncomeSrc,~ADM1_NAME+Gender,~Gender+IncomeSrc),
                    population.margins=list(calbrDFIncomeSrc[,c(1,3,4,2)]*totPop,calbrDFGender*totPop,calbrDFGenderIncome[,c(1,3,4,2)]*totPop),
                    control = list(maxit = 100, epsilon = 1, verbose=FALSE) )

summary(svymVAM2)
svyby(~HDDS, by=~ADM1_NAME, design=svymVAM2, FUN=svymean)



```

```{r}
#examining prevalence on percentile calculation of HDDS threshold

thrF2F <- svyquantile(~HDDS,quantiles=0.66666666,design=svyF2F)[1]
thrmVAM <- svyquantile(~HDDS,quantiles=0.66666666,design=svymVAM2)[1]

svyF2F$variables$HDDS_YN <- svyF2F$variables$HDDS >= thrF2F
svymVAM2$variables$HDDS_YN <- svymVAM2$variables$HDDS >= thrmVAM

svyby(~HDDS_YN, by=~ADM1_NAME, design=svyF2F, FUN=svymean)
svyby(~HDDS_YN, by=~ADM1_NAME, design=svymVAM2, FUN=svymean)

#as above but disaggregating by ADM1

thrF2FI <- svyquantile(~HDDS,quantiles=0.66666666,subset(svyF2F,ADM1_NAME=='Inhambane'))[1]
thrF2FG <- svyquantile(~HDDS,quantiles=0.66666666,subset(svyF2F,ADM1_NAME=='Gaza'))[1]
thrmVAMI <- svyquantile(~HDDS,quantiles=0.66666666,subset(svymVAM2,ADM1_NAME=='Inhambane'))[1]
thrmVAMG <- svyquantile(~HDDS,quantiles=0.66666666,subset(svymVAM2,ADM1_NAME=='Gaza'))[1]
# no point continuing further as thresholds same for ADM1 as overall per mVAM

svyF2F$variables$HDDS_YN <- svyF2F$variables$HDDS >= thrF2F
svymVAM2$variables$HDDS_YN <- svymVAM2$variables$HDDS >= thrmVAM

svyby(~HDDS_YN, by=~ADM1_NAME, design=svyF2F, FUN=svymean)
svyby(~HDDS_YN, by=~ADM1_NAME, design=svymVAM2, FUN=svymean)

```